# Exercise 2: Objects, Data Types, and Variables in R
`r Sys.Date()`

```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```



## Task 1: Create Numeric Variables

Create two numeric variables, `num1` and `num2`, and assign them any numeric
values.

Your code here:
## Task 2: Create Character Variables

Create two character variables, `char1` and `char2`, and assign them any
strings.

Your code here:
## Task 3: Create Logical Variables

Create two logical variables, `logical1` and `logical2`, and assign them any
logical values.

Your code here:
## Task 4: Create Integer Variables

Create two integer variables, `int1` and `int2`, and assign them any integer
values.

Your code here:
## Task 5: Create Complex Variables

Create two complex variables, `complex1` and `complex2`, and assign them any
complex values.

Your code here:
## Task 6: Explore a dataset.

Load the dataset `mtcars` and explore its structure using the `str` function.
What can be inferred from the structure of the dataset?

Hint: to access a single column of a data frame, you can use the `$`
operator. For example, to access the `mpg` column of the `mtcars` dataset,
you can use `mtcars$mpg`.

Your code and/or comments here:

That's it for Exercise 2! Well done!


```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```

