# Exercise 2 Solutions: Objects, Data Types, and Variables in R
`r Sys.Date()`

```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```



## Task 1: Create Numeric Variables

Create two numeric variables, `num1` and `num2`, and assign them any numeric
values.

Your code here:

```{r}
num1 <- 10.5
num2 <- 7.2
```

## Task 2: Create Character Variables

Create two character variables, `char1` and `char2`, and assign them any
strings.

Your code here:

```{r}
char1 <- "Hello"
char2 <- "World"
```

## Task 3: Create Logical Variables

Create two logical variables, `logical1` and `logical2`, and assign them any
logical values.

Your code here:

```{r}
logical1 <- TRUE
logical2 <- FALSE
```

## Task 4: Create Integer Variables

Create two integer variables, `int1` and `int2`, and assign them any integer
values.

Your code here:

```{r}
int1 <- 5
int2 <- -3
```

## Task 5: Create Complex Variables

Create two complex variables, `complex1` and `complex2`, and assign them any
complex values.

Your code here:

```{r}
complex1 <- 2 + 3i
complex2 <- -1 + 4i
```

## Task 6: Explore a dataset.

Load the dataset `mtcars` and explore its structure using the `str` function.
What can be inferred from the structure of the dataset?

Hint: to access a single column of a data frame, you can use the `$`
operator. For example, to access the `mpg` column of the `mtcars` dataset,
you can use `mtcars$mpg`.

Your code and/or comments here:
Load the mtcars dataset

```{r}
data(mtcars)
str(mtcars)
```

The mtcars dataset has 32 observations and 11 variables. The variables are
all numeric, representing various attributes of cars such as miles per gallon
(mpg), number of cylinders (cyl), horsepower (hp), and weight (wt).

```{r}
class(mtcars$gear)
```

The `gear` variable is by default an numeric variable, but it represents the
number of forward gears in the car. It would make more sense to treat it as a
an integer variable, as the number of gears is a whole number. In future
lectures, we will learn about factors, which are used to represent
categorical variables in R. This would be a better choice for the `gear`
variable, which has a natural ordering but is not a continuous numeric
variable.

That's it for Exercise 2! Well done!


```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```

