# Lecture 2: Objects, Data Types, and Variables in R
`r Sys.Date()`

```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```


In this lecture, we will learn about objects, data types, and variables in R.

Objects are the basic building blocks of R, and they can store data,
functions, or other objects. R has several built-in data types, including
numeric, character, logical, integer, and complex.

Variables...

- are used to store objects in R, and they can be assigned using the
  assignment operator `<-`. (or `=`, but `<-` is preferred!)
- in R are case-sensitive, so `myVar` is not the same as `myvar`.
- have names in R which can contain letters, numbers, underscores, and dots,
  but they cannot start with a number.
- can be assigned to objects, data, functions, or other variables.

Let's create some variables in R!

Create a numeric variable

```{r}
my_num <- 42
```

Create a character variable

```{r}
my_char <- "Hello, World!"
```

Create a logical variable

```{r}
my_logical <- TRUE
```

Create an integer variable

Note: In R, integers are specified by adding an `L` to the end of the number
(`L` stands for "long integer"). This tells R to treat the number as an
integer rather than a numeric value.

```{r}
my_int <- 42L
```

Create a complex variable

Note: In R, complex numbers are specified using the `i` suffix. The real part
is separated from the imaginary part by a `+` sign. We won't be using complex
numbers at all in this course, but it's good to know they exist!

```{r}
my_complex <- 3 + 4i
```

Display the values of the variables

```{r}
print(my_num)
print(my_char)
print(my_logical)
print(my_int)
print(my_complex)
```

## Data Types

R has several built-in data types, including:

- Numeric: Represents real numbers (e.g., 3.14).
- Character: Represents text data (e.g., "Hello, World!").
- Logical: Represents boolean values (`TRUE` or `FALSE`).
- Integer: Represents whole numbers (e.g., 42L).
- Complex: Represents complex numbers (e.g., 3 + 4i).

Let's check the data types of the variables we created earlier.

Note: The `class` function is used to check the data type of an object in R.
It returns the class or data type of the object.

```{r}
class(my_num)
class(my_char)
class(my_logical)
class(my_int)
class(my_complex)
```

Note: The `typeof` function is used to check the internal type of an object
in R. It returns the internal type of the object. For example, numeric,
character, logical, integer, etc.

```{r}
typeof(my_num)
typeof(my_char)
typeof(my_logical)
typeof(my_int)
typeof(my_complex)
```

Note: The `mode` function is used to check the storage mode of an object in
R. It returns the storage mode of the object. For example, numeric,
character, logical, integer, etc.

```{r}
mode(my_num)
mode(my_char)
mode(my_logical)
mode(my_int)
mode(my_complex)
```

Note: The `is.numeric` function is used to check if an object is of the
numeric data type. It returns `TRUE` if the object is numeric and `FALSE`
otherwise. This is useful when you want to check if an object is numeric
before performing numeric operations on it (e.g., addition, subtraction,
multiplication, division).

```{r}
is.numeric(my_num)
is.numeric(my_char)
is.numeric(my_logical)
is.numeric(my_int)
is.numeric(my_complex)
```

Note: The `is.character` function is used to check if an object is of the
character data type. It returns `TRUE` if the object is character and `FALSE`
otherwise.

```{r}
is.character(my_num)
is.character(my_char)
is.character(my_logical)
is.character(my_int)
is.character(my_complex)
```

Note: The `is.logical` function is used to check if an object is of the
logical data type. It returns `TRUE` if the object is logical and `FALSE`
otherwise. This is useful when you want to check if an object is logical
before performing logical operations on it (e.g., AND, OR, NOT).

```{r}
is.logical(my_num)
is.logical(my_char)
is.logical(my_logical)
is.logical(my_int)
is.logical(my_complex)
```

That's it for this example! In the next lecture, we will learn about
arithmetic operations in R.


```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```

