# Exercise 8 Solutions: Data Frames in R
`r Sys.Date()`

```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```



## Task 1: Creating Data Frames

Create the following data frames and assign them to variables:

1. Create a data frame with the following columns:
   - name: "Alice", "Bob", "Charlie", "David", "Eve"
   - age: 25, 30, 35, 40, 45
   - employed: TRUE, FALSE, TRUE, FALSE, TRUE Assign the data frame to a
   variable called `df1`.

2. Create a data frame with the following columns:
   - city: "New York", "Los Angeles", "Chicago", "Houston", "Phoenix"
   - population: 8537673, 3976322, 2720546, 2296224, 1660272
   - state: "New York", "California", "Illinois", "Texas", "Arizona" Assign
   the data frame to a variable called `df2`.

Your code here:

```{r}
df1 <- data.frame(
    name = c("Alice", "Bob", "Charlie", "David", "Eve"),
    age = c(25, 30, 35, 40, 45),
    employed = c(TRUE, FALSE, TRUE, FALSE, TRUE)
)

df2 <- data.frame(
    city = c("New York", "Los Angeles", "Chicago", "Houston", "Phoenix"),
    population = c(8537673, 3976322, 2720546, 2296224, 1660272),
    state = c("New York", "California", "Illinois", "Texas", "Arizona")
)
```

## Task 2: Accessing Data Frame Elements

Use indexing to perform the following operations:

1. Access the element in the second row and third column of `df1` and assign
   it to a variable called `element1`.

2. Access the value of the "population" column in the fourth row of `df2` and
   assign it to a variable called `element2`.

Your code here:

```{r}
element1 <- df1[2, 3]
element2 <- df2[4, "population"]
```

## Task 3: Manipulating Data Frames

Perform the following operations on the data frames:

1. Add a new column to `df1` called "gender" with the values "female",
   "male", "male", "female", "female".

2. Change the value of the "state" column in the third row of `df2` to
   "Michigan".

Your code here:

```{r}
df1$gender <- c("female", "male", "male", "female", "female")
df2[3, "state"] <- "Michigan"
```

## Task 4: Display the Results

Print the values of all the variables created in Task 1, Task 2, and Task 3.

Your code here:

```{r}
print(df1)
print(df2)
print(element1)
print(element2)
```

