# Exercise 8: Data Frames in R
`r Sys.Date()`

```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```



## Task 1: Creating Data Frames

Create the following data frames and assign them to variables:

1. Create a data frame with the following columns:
   - name: "Alice", "Bob", "Charlie", "David", "Eve"
   - age: 25, 30, 35, 40, 45
   - employed: TRUE, FALSE, TRUE, FALSE, TRUE

Assign the data frame to a variable called `df1`.

2. Create a data frame with the following columns:
   - city: "New York", "Los Angeles", "Chicago", "Houston", "Phoenix"
   - population: 8537673, 3976322, 2720546, 2296224, 1660272
   - state: "New York", "California", "Illinois", "Texas", "Arizona"

Assign the data frame to a variable called `df2`.

Your code here:
## Task 2: Accessing Data Frame Elements

Use indexing to perform the following operations:

1. Access the element in the second row and third column of `df1` and assign
   it to a variable called `element1`.

2. Access the value of the "population" column in the fourth row of `df2` and
   assign it to a variable called `element2`.

Your code here:
## Task 3: Manipulating Data Frames

Perform the following operations on the data frames:

1. Add a new column to `df1` called "gender" with the values "female",
   "male", "male", "female", "female".

2. Change the value of the `employed` column in the second row of `df1` to
   either `"currently employed"` and `"not employed"`, i.e., a character
   vector rather than a logical vector. Attempt doing this using the logical
   values themselves rather than "hardcoding" it one-by-one.

3. Change the value of the "state" column in the third row of `df2` to
   "Michigan".

4. Change the values of the population column in `df2` to millions of people
   rather than the full range of numbers.

Hint: For task 4 it might be useful to incorporate the built-in `round()`
function in R.

Your code here:

That's it for Exercise 8! Well done!


```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```

