# Exercise 11: Working with Factors in R
`r Sys.Date()`

```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```



## Task 1: Creating a Factor

Consider the following vector of fruit names:


```{r}
fruit_vector <- c("apple", "banana", "cherry", "apple", "banana", "cherry")
```


Create a factor called `fruit_factor` from the `fruit_vector` using the
`factor()` function.

Your code here:
## Task 2: Specifying Factor Levels


Consider the following vector of T-shirt sizes:


```{r}
size_vector <- c("S", "M", "L", "M", "S", "XL", "L", "S", "M")
```


Create a factor called `size_factor_specified` from the `size_vector` using
the `factor()` function. Specify the levels of the factor as "S", "M", "L",
and "XL".

Your code here:
## Task 3: Accessing Factor Levels


Access the levels of the `size_factor_specified` factor using the `levels()`
function and assign the result to a variable called `factor_levels`.

Your code here:
## Task 4: Modifying Factor Levels


Modify the levels of the `size_factor_specified` factor by changing the order
to "M", "S", "XL", and "L". Assign the modified factor to a variable called
`modified_factor`.

Your code here:
## Task 5: Factor Operations


Perform the following operations on the `size_factor_specified` factor and
assign the results to new variables:

1. Compute the frequency of each level in the factor and assign the result to
   a variable called `level_frequency`.

2. Compute the cumulative frequency of each level in the factor and assign
   the result to a variable called `cumulative_frequency`.

Your code here:
## Task 6: Using factors with real data

Consider the `mpg` data set from the ggplot2 package (install the package and
load it, if not already installed)

```{r}
library(ggplot2)
data(mpg)
```

You may read up on what each column is describing by using

```{r eval=FALSE}
?mpg
```

There is a function in R called `unique()`. It tells us how many unique
values a certain vector contains. For instance, the following code gives us
information about all unique values of the cylinders, which is only 4 in
total.

```{r}
unique(mpg$cyl)
```

The normal case for when loading data into R, such as a .csv (comma seperated
value) file, is that factors are not included.

For this task, give suggestions on which variables can reasonably be turned
into factors, and, where applicable provide factor levels or even ordered
factors. Transform the columns accordingly!

Finally, given the transformed data set, provide the following.

1. Cars with more than 4 cylinders but less than 8 cylinders.

2. Cars with 4 or 6 cylinders and a highway mileage of more than 30 miles per
  gallon.

3. The average city mileage for cars with 4, 6, or 8 cylinders.

Your code here:
That's it for Exercise 11! Great job!


```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")

htmltools::includeHTML("../../index_exercises.html")
```

