# Exercise 11: Working with Factors in R
`r Sys.Date()`

```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```



## Task 1: Creating a Factor

Consider the following vector of fruit names:


```{r}
fruit_vector <- c("apple", "banana", "cherry", "apple", "banana", "cherry")
```


Create a factor called `fruit_factor` from the `fruit_vector` using the
`factor()` function.

Your code here:
## Task 2: Specifying Factor Levels


Consider the following vector of T-shirt sizes:


```{r}
size_vector <- c("S", "M", "L", "M", "S", "XL", "L", "S", "M")
```


Create a factor called `size_factor_specified` from the `size_vector` using
the `factor()` function. Specify the levels of the factor as "S", "M", "L",
and "XL".

Your code here:
## Task 3: Accessing Factor Levels


Access the levels of the `size_factor_specified` factor using the `levels()`
function and assign the result to a variable called `factor_levels`.

Your code here:
## Task 4: Modifying Factor Levels


Modify the levels of the `size_factor_specified` factor by changing the order
to "M", "S", "XL", and "L". Assign the modified factor to a variable called
`modified_factor`.

Your code here:
## Task 5: Factor Operations


Perform the following operations on the `size_factor_specified` factor and
assign the results to new variables:

1. Compute the frequency of each level in the factor and assign the result to
   a variable called `level_frequency`.

2. Compute the cumulative frequency of each level in the factor and assign
   the result to a variable called `cumulative_frequency`.

Your code here:
## Task 6: Displaying Results

Display the factor `fruit_factor`, the modified factor `modified_factor`, the
factor levels `factor_levels`, the level frequency `level_frequency`, and the
cumulative frequency `cumulative_frequency` using the `print` function.

Your code here:
That's it for Exercise 11! Great job!


```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```

