# Exercise 7: Matrices in R
`r Sys.Date()`

```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```



## Task 1: Creating Matrices

Create the following matrices and assign them to variables:

1. Create a matrix with the following elements: 1, 2, 3, 4, 5, 6 and assign
   it to a variable called `matrix1`. The matrix should have 2 rows and 3
   columns.

2. Create a matrix with the following elements: 10, 20, 30, 40 and assign it
   to a variable called `matrix2`. The matrix should have 2 rows and 2
   columns. Use row names "A" and "B" and column names "C" and "D",
   respectively.

Hint: Either include the argument `dimnames` in the matrix function or use
the `rownames` and `colnames` functions to set the row and column names. The
`dimnames` argument takes a list with two elements: the row names and the
column names.

Your code here:
## Task 2: Accessing Matrix Elements

Use indexing to perform the following operations:

1. Access the element in the first row and second column of `matrix1` and
   assign it to a variable called `element1`.

2. Access the column "D" and second row of `matrix2` and assign it to a
   variable called `element2`.

Your code here:
## Task 3: Manipulating Matrices

Perform the following operations on the matrices:

1. Add a new row to `matrix1` with the values 7, 8, 9.

2. Change the value of the "C" column in the first row of `matrix2` to 50.

Your code here:

That's it for Exercise 7! Well done!


```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```

