# Exercise 7 Solutions: Matrices in R
`r Sys.Date()`

```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```



## Task 1: Creating Matrices

Create the following matrices and assign them to variables:

1. Create a matrix with the following elements: 1, 2, 3, 4, 5, 6 and assign
   it to a variable called `matrix1`. The matrix should have 2 rows and 3
   columns.

2. Create a matrix with the following named elements: "A" with value 10, "B"
   with value 20, "C" with value 30, "D" with value 40 and assign it to a
   variable called `matrix2`. The matrix should have 2 rows and 2 columns.

Your code here:

```{r}
matrix1 <- matrix(c(1, 2, 3, 4, 5, 6), nrow = 2, ncol = 3)
matrix2 <- matrix(c(10, 20, 30, 40), nrow = 2, ncol = 2, dimnames = list(NULL, c("A", "B", "C", "D")))
```

## Task 2: Accessing Matrix Elements

Use indexing to perform the following operations:

1. Access the element in the first row and second column of `matrix1` and
   assign it to a variable called `element1`.

2. Access the value of the "B" element in the second row of `matrix2` and
   assign it to a variable called `element2`.

Your code here:

```{r}
element1 <- matrix1[1, 2]
element2 <- matrix2[2, "B"]
```

## Task 3: Manipulating Matrices

Perform the following operations on the matrices:

1. Add a new row to `matrix1` with the values 7, 8, 9.

2. Change the value of the "C" element in the first row of `matrix2` to 50.

Your code here:

```{r}
matrix1 <- rbind(matrix1, c(7, 8, 9))
matrix2[1, "C"] <- 50
```

## Task 4: Display the Results

Print the values of all the variables created in Task 1, Task 2, and Task 3.

Your code here:

```{r}
print(matrix1)
print(matrix2)
print(element1)
print(element2)
```

That's it for Exercise 7! Well done!


```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```

