# Exercise 6: Lists in R
`r Sys.Date()`

```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```



## Task 1: Creating Lists

Create the following lists and assign them to variables:

1. Create a list with the following elements: 10, "red", TRUE, 3.14 and
   assign it to a variable called `my_list`.

2. Create a list with the following named elements: "name" with value "John",
   "age" with value 25, "city" with value "New York" and assign it to a
   variable called `person`.

Your code here:
## Task 2: Accessing List Elements

Use indexing to perform the following operations:

1. Access the second element of the first list and assign it to a variable
   called `list_element`.

2. Access the value of the "age" element in the second list and assign it to
   a variable called `age`.

Your code here:
## Task 3: Manipulating Lists

Perform the following operations on the lists:

1. Add a new element to the first list with the value "blue" and assign the
   modified list to a new variable called `modified_list`.

2. Change the value of the "city" element in the second list to "San
   Francisco".

Your code here:

That's it for Exercise 6! Well done!


```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```

