---
title: "Lecture 8: Data Frames in R"
output: github_document
date: "2024-08-23"
---

In this lecture, we will learn about data frames in R.
Data frames are a fundamental data structure in R that allow us to store and manipulate tabular data.
They are similar to matrices, but with additional features that make them more flexible and powerful.

## Data Frames in R

Data frames...

- are two-dimensional arrays in R that can store different types of data.
- are created using the `data.frame()` function, which takes named vectors as arguments.
- can have columns of different types (e.g., numeric, character, logical). 
  This differs from matrices, which can only store elements of the same type.
- can be indexed using row and column indices, as well as column names.
- are commonly used to represent data sets in R.

Let's create a data frame in R!

Create a data frame with named vectors
The `data.frame()` function takes named vectors as arguments.
Each named vector becomes a column in the data frame.
We will discuss functions and arguments in more detail in the next lecture.
For now, focus on understanding how to create a data frame in R.
```{r}
my_data_frame <- data.frame(
  name = c("Alice", "Bob", "Charlie", "David", "Eve"),
  age = c(25, 30, 35, 40, 45),
  employed = c(TRUE, FALSE, TRUE, FALSE, TRUE)
)
```

Notice how we have created a data frame with three columns: `name`, `age`, and `employed`.
The name column contains character values, the age column contains numeric values, and the employed column contains logical values.
This demonstrates how data frames can store columns of different types.
Also note that we used named vectors to create the data frame, with the names becoming the column names.

### Display the data frame

The numbers in the leftmost column are row indices, which are automatically assigned by R.
```{r}
print(my_data_frame)
```

It is possible to assign row names
```{r}
rownames(my_data_frame) <- c("row_1", "row_2", "row_3", "row_4", "row_5")
print(my_data_frame)
```

Let's reset the row names for now
```{r}
rownames(my_data_frame) <- NULL
```

## Accessing elements of a data frame

Elements of a data frame can be accessed using row and column indices, as well as column names.
We can use the square brackets `[]` to access elements of a data frame.
This is analogous to how we access elements of matrices.

Access the element in the first row and second column
```{r}
print(my_data_frame[1, 2])
```

Access the element in the second row and third column
```{r}
print(my_data_frame[2, 3])
```

Accessing entire rows or columns of a data frame is similar to accessing elements of a matrix.
I refer you to the previous lecture for more information on this topic, and we will not repeat the examples here.

We can also change column names
```{r}
colnames(my_data_frame) <- c("full_name", "years", "is_employed")
print(my_data_frame)
```

We can also add new columns to a data frame
For example, let's add a new column called `height` to the data frame.
The new column will contain numeric values representing the height of each individual.
We can add a new column to a data frame by assigning a vector of values to a new column name.
The length of the vector must match the number of rows in the data frame.
The `$` sign is used to access columns in a data frame.
```{r}
my_data_frame$height <- c(160, 170, 180, 190, 200)
```

To see where the `$` sign comes from, let's print the structure of the data frame
The structure of the data frame shows the names of the columns and their types.
```{r}
print(str(my_data_frame))
```

We can also summarize the data frame
The summary() function provides a summary of the data frame, including the number of observations, 
the number of missing values, and the distribution of values for each column.
```{r}
summary(my_data_frame)
```

That's it for this example! In the next lecture, we will learn about functions and arguments in R.
