# Exercise 5 Solutions: Vectors in R
`r Sys.Date()`


## Task 1: Creating Vectors

Create the following vectors and assign them to variables:

1. Create a numeric vector with values 10, 20, 30, 40, 50 and assign it to a
   variable called `numeric_vector`.

2. Create a character vector with values "red", "green", "blue", "yellow",
   "orange" and assign it to a variable called `character_vector`.

3. Create a logical vector with values TRUE, FALSE, TRUE, FALSE, TRUE and
   assign it to a variable called `logical_vector`.

Your code here:

```{r}
numeric_vector <- c(10, 20, 30, 40, 50)
character_vector <- c("red", "green", "blue", "yellow", "orange")
logical_vector <- c(TRUE, FALSE, TRUE, FALSE, TRUE)
```

## Task 2: Accessing Vector Elements

Use indexing to perform the following operations:

1. Access the second element of the numeric vector and assign it to a
   variable called `numeric_element`.

2. Access the third element of the character vector and assign it to a
   variable called `character_element`.

3. Access the last element of the logical vector and assign it to a variable
   called `logical_element`.

Your code here:

```{r}
numeric_element <- numeric_vector[2]
character_element <- character_vector[3]
logical_element <- logical_vector[length(logical_vector)]
```

## Task 3: Manipulating Vectors

Perform the following operations on the vectors:

1. Add 5 to each element of the numeric vector and assign the result to a new
   variable called `numeric_vector_plus_5`.

2. Concatenate the character vector with itself and assign the result to a
   new variable called `character_vector_concatenated`.

3. Negate the logical vector and assign the result to a new variable called
   `logical_vector_negated`.

Your code here:

```{r}
numeric_vector_plus_5 <- numeric_vector + 5
character_vector_concatenated <- c(character_vector, character_vector)
logical_vector_negated <- !logical_vector
```

## Task 4: Display the Results

Print the values of all the variables created in Task 1, Task 2, and Task 3.

Your code here:

```{r}
print(numeric_vector)
print(character_vector)
print(logical_vector)
print(numeric_element)
print(character_element)
print(logical_element)
print(numeric_vector_plus_5)
print(character_vector_concatenated)
print(logical_vector_negated)
```

