# Exercise 10: Indexing using Logical Vectors in R
`r Sys.Date()`

```{r echo = FALSE}
htmltools::includeHTML("../../index_lectures.html")
htmltools::includeHTML("../../index_exercises.html")
```



## Task 1: Creating Logical Vectors

Consider the following vector of numeric values:


```{r}
my_vector <- c(1, 2, 3, 4, 5)
```


Create the following logical vectors:

1. Create a logical vector called `logical_vector1` that indicates whether
   each element of `my_vector` is less than or equal to `3`.

2. Create a logical vector called `logical_vector2` that indicates whether
   each element of `my_vector` is equal to `3`.

3. Create a logical vector called `logical_vector3` that indicates whether
   each element of `my_vector` is greater than `2` and less than `5`.

Your code here:
## Task 2: Indexing using Logical Vectors


Use the logical vectors to index elements of `my_vector` and assign the
results to new variables.

1. Index `my_vector` using `logical_vector1` and assign the result to a
   variable called `result_vector1`.

2. Index `my_vector` using `logical_vector2` and assign the result to a
   variable called `result_vector2`.

3. Index `my_vector` using `logical_vector3` and assign the result to a
   variable called `result_vector3`.

Your code here:
## Task 4: Logical operators without creating logical vectors

Index `my_vector` directly using the following conditions without creating

1. Index the vector using the condition `my_vector > 3` and assign the result

2. Index the vector using the condition `my_vector == 3` and assign the
   result

3. Index the vector using the condition `my_vector <= 3` and assign the
   result

Your code here:
## Task 5: Displaying Results

Display the result vectors using the `print` function.

Your code here:
That's it for Exercise 10! Well done!
