# Exercise 10 Solutions: Indexing using Logical Vectors in R
`r Sys.Date()`


## Task 1: Creating Logical Vectors

Consider the following vector of numeric values:


```{r}
my_vector <- c(1, 2, 3, 4, 5)
```


Create the following logical vectors:

1. Create a logical vector called `logical_vector1` that indicates whether
   each element of `my_vector` is less than or equal to `3`.


```{r}
logical_vector1 <- my_vector <= 3
```

2. Create a logical vector called `logical_vector2` that indicates whether
   each element of `my_vector` is equal to `3`.


```{r}
logical_vector2 <- my_vector == 3
```

3. Create a logical vector called `logical_vector3` that indicates whether
   each element of `my_vector` is greater than `2` and less than `5`.


```{r}
logical_vector3 <- my_vector > 2 & my_vector < 5
```

## Task 2: Indexing using Logical Vectors


Use the logical vectors to index elements of `my_vector` and assign the
results to new variables.

1. Index `my_vector` using `logical_vector1` and assign the result to a
   variable called `result_vector1`.


```{r}
result_vector1 <- my_vector[logical_vector1]
```

2. Index `my_vector` using `logical_vector2` and assign the result to a
   variable called `result_vector2`.


```{r}
result_vector2 <- my_vector[logical_vector2]
```

3. Index `my_vector` using `logical_vector3` and assign the result to a
   variable called `result_vector3`.


```{r}
result_vector3 <- my_vector[logical_vector3]
```

## Task 4: Logical operators without creating logical vectors

Index `my_vector` directly using the following conditions without creating

1. Index the vector using the condition `my_vector > 3` and assign the result


```{r}
result_vector4 <- my_vector[my_vector > 3]
```

2. Index the vector using the condition `my_vector == 3` and assign the
   result


```{r}
result_vector5 <- my_vector[my_vector == 3]
```

3. Index the vector using the condition `my_vector <= 3` and assign the
   result


```{r}
result_vector6 <- my_vector[my_vector <= 3]
```

## Task 5: Displaying Results

Display the result vectors using the `print` function.


```{r}
print(result_vector1)
print(result_vector2)
print(result_vector3)
print(result_vector4)
print(result_vector5)
print(result_vector6)
```

That's it for Exercise 10! Well done!
